Differential Testing Runtime Engines--Lessons Learned from the JavaScript Domain

### 2018-07-31 paper/paper.tex
pass on false positives

The overarching goal of our study is to identify the ability of
cross-engine differential testing to find bugs in \js\ engines.  We
analyzed the impact of two orthogonal dimensions in this study: test
mining and fuzzing. The first dimension focuses on the impact of
inputs, mined from the web, in bug finding whereas the second
dimension focuses on the impact of fuzzing these inputs.

In the following, we describe the methodology we used in this
experiment. Recall that our tool outputs a set of buckets, that each
bucket includes a set of warnings, that each warning is related to one
file, and that a bucket is of ``lo'' or ``hi'' importance, according
to the heuristic we defined. Figure~\ref{fig:distribution} shows the
distribution of number of warnings per bucket. We use the the label
``nofuzz'' to refer to the experiment that analyzed the impact of test
mining as we do not use fuzzing in that experiment and use the names
of the fuzzing tools to refer to the results obtained with those
tools. We inspected each and every bucket for bugs, but observe that
the number of files per bucket is very high in some cases (\eg{},
nofuzz [hi]). As such, it would be impractical to manually inspect all
the files in the bucket. For that reason, we only inspected one file
per bucket. For the cases we found the warning suspicious, we analyzed
the parts of the documentation related to the problem and, if still
suspicious, we looked on the bug tracker of the affected engine for
potential duplicates. If none was reported, we filed a bug report in
the bug tracker including the test input that manifested the potential
problem and explaining the reasons we were suspicious. In some cases,
we used the Mozila lithium tool~\cite{lithium} to minimize the test
case. For the cases of false positives, we classified the reason for
the misclassification and moved to the next
bucket. Table~\ref{tab:summary-of-results} summarizes our results. It
shows, for each execution mode and category of bucket (\ie{}, hi or
lo), the total number of files involved, the number of buckets
reported, and the percentage of those that resulted in a bug
report. \Fix{elaborate summary} We elaborate those results in the
following.

\begin{table}[t]
  \centering
  \caption{\label{tab:summary-of-results}Summary of results.}
  \begin{tabular}{ccrrr}
    \toprule
    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{2}{c}{buckets} \\
    \cline{4-5}    
    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\% positive} \\
    \midrule
    \multirow{2}{*}{no-fuzz} & lo & \nofuzzFilesLO{} & \nofuzzLOTotal{} & 34.3\% \\
    & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & 70\% \\
    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
    & hi & \Fix{.} & \Fix{.} & \Fix{.} \\
    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} \\
                             & hi & \Fix{.} & \Fix{.} & \Fix{.} \\    
    \bottomrule     
  \end{tabular}
\end{table}

@@

%%  LocalWords:  bytecodes JScript Ecma

>>>>

The overarching goal of our study is to identify the ability of
cross-engine differential testing to find bugs in \js\ engines.  We
analyzed the impact of two orthogonal dimensions in this study: test
mining and fuzzing. The first dimension focuses on the impact of
inputs, mined from the web, in bug finding whereas the second
dimension focuses on the impact of fuzzing those inputs.

In the following, we describe the methodology we used in this
experiment. Recall that our tool outputs a set of buckets, that each
bucket includes a set of warnings, that each warning is related to one
file, and that a bucket is of ``lo'' or ``hi'' importance, according
to the heuristic we defined. Figure~\ref{fig:distribution} shows the
distribution of number of warnings per bucket. We use the the label
``nofuzz'' to refer to the experiment that analyzed the impact of test
mining as we do not use fuzzing in that experiment and use the names
of the fuzzing tools to refer to the results obtained with those
tools. We inspected each and every bucket for bugs, but observe that
the number of files per bucket is very high in some cases (\eg{},
nofuzz [hi]). As such, it would be impractical to manually inspect all
the files in the bucket. For that reason, we only inspected one file
per bucket. For the cases we found the warning suspicious, we analyzed
the parts of the documentation related to the problem and, if still
suspicious, we looked on the bug tracker of the affected engine for
potential duplicates. If none was reported, we filed a bug report
including the test input that manifested the potential problem and
explaining the reasons we were suspicious. In some cases, we used the
Mozila lithium tool~\cite{lithium} to minimize the test case. For the
cases of false positives, we identified the source of false positive
and moved to the next bucket. Table~\ref{tab:summary-of-results}
summarizes our results. It shows, for each execution mode and category
of bucket (\ie{}, hi or lo), the total number of files involved, the
number of buckets reported by our infrastructure, the number of those
that we classified as bug-revealing, and the number of those that we
filed a bug report. The difference between the last two columns
indicate the number of duplicates, \ie{}, the cases of
already-reported bugs. As expected, the hit ratio for the ``hi'' group
is higher.

\begin{table}[t]
  \centering
  \caption{\label{tab:summary-of-results}Summary of results.}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{3}{c}{buckets} \\
    \cline{4-6}    
    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\# pos.} &
    \multicolumn{1}{c}{\# pos. filed} \\
    \midrule
    \multirow{2}{*}{nofuzz} & lo & \nofuzzFilesLO{} &  \nofuzzLOTotal{} & \Fix{.} & 11 (34) \\
    & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & \Fix{.} & \Fix{108 (-)} \\
    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
    & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
                             & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\    
    \bottomrule     
  \end{tabular}
\end{table}

Table~\ref{tab:false-positives} shows the distribution of false
positives per source. A false positive is a bucket that did not reveal
a bug. We identified five sources of imprecision. The source ``not yet
implemented'' indicates that the engine does not implement some part
of the specification. For example, at the time of writing, Chakra does
not implement various properties from the \CodeIn{Symbol} object. The
source ``invalid input'' indicates that the test violated some part of
the specification. For example, the test indirectly invoked some
function with unexpected arguments\Fix{provide concrete example}. In
all cases that we analyzed, that happened because fuzzing produced an
invalid test input. Note that no false positives of this kind appears
under the column nofuzz. The source ``timeout/ome'' indicates that the
test times out (we used a 3s time budget) or runs out of memory. That
happens because engines implement different set of optimizations. For
example, only \jsc{} implements tail-call optimization to avoid tail
recursion. Consequently, for a certain input, it finishes execution
quickly whereas other engines time out. The source
``implementation-dependent'' is as defined in
Section~\ref{sec:imp-dep-behavior}.\Fix{provide concrete example} The
source ``future feature'' corresponds to the case where some feature
will be part of the spec in the future but implementing it is
facultative.\Fix{provide concrete example}

\begin{table}[t]
  \centering
  \caption{\label{tab:false-positives}Distribution of false
    positives buckets per source.}
  \begin{tabular}{crrr}
    \toprule
              & nofuzz & \radamsa\ & \quickfuzz\ \\
%    duplicate & 63      & - & - \\
    not yet implemented & 8 & - & - \\
    invalid input & 0 & - & - \\
    timeout/ome & 13 & - & - \\
    implementation-dependent & 3 & - & - \\
    future feature & 3 & - & - \\
    \bottomrule     
  \end{tabular}
\end{table}

@@

%%  LocalWords:  bytecodes JScript Ecma ome
